From Education to Entrepreneurship

### 2014-12-02 index.Rmd
second commit
Added web content

---
title: 'Index'
author: "Sam"
date: "November 20, 2014"
output: html_document
---

### Under Construction

>>>>

---
title: 'From Education to Entrepreneurship'
author: "Sam"
date: "November 20, 2014"
output: html_document
---

### Under construction, but here's a preview

```{r echo =FALSE, cache=TRUE, include=FALSE, results='asis'}

# Library required packages
library(googleVis)
library(countrycode)
library(repmis)

# Import GEM data frame
PerceivedOpportunities <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/PerceivedOpportunities.csv", header = TRUE, cache = FALSE, na.strings = "-")

## Add country codes and place new column at beginning of the data frame
# Create a vector of country codes
D2 <- countrycode(PerceivedOpportunities$Country, "country.name", "iso2c")

# Create a new column and insert the country code vector
PerceivedOpportunities$new.col <- D2

# Reorder columns so country code is first
D3 <- PerceivedOpportunities[,c(15,1:14)]

# Rename first column
D4 <- plyr::rename(x = D3, 
                   replace = c("new.col" = "iso2c"))

# Remove X's in D4 year columns
names(D4) <- gsub("X", "", names(D4))

# Set columns as numeric
D4[,"2001"] <- as.numeric(D4[,"2001"])
D4[,"2002"] <- as.numeric(D4[,"2002"])
D4[,"2003"] <- as.numeric(D4[,"2003"])
D4[,"2004"] <- as.numeric(D4[,"2004"])
D4[,"2005"] <- as.numeric(D4[,"2005"])
D4[,"2006"] <- as.numeric(D4[,"2006"])
D4[,"2007"] <- as.numeric(D4[,"2007"])
D4[,"2008"] <- as.numeric(D4[,"2008"])
D4[,"2009"] <- as.numeric(D4[,"2009"])
D4[,"2010"] <- as.numeric(D4[,"2010"])
D4[,"2011"] <- as.numeric(D4[,"2011"])
D4[,"2012"] <- as.numeric(D4[,"2012"])
D4[,"2013"] <- as.numeric(D4[,"2013"])

# Generate a new column with mean of all other columns
D4$mean <- rowMeans(subset(D4, select = c("2001", "2002", "2003", "2004", "2005", "2006", "2007", "2008",
                                          "2009", "2010", "2011", "2012", "2013")), na.rm = TRUE)

# Drop year columns, leaving only mean column
D4$'2001' <- NULL
D4$'2002' <- NULL
D4$'2003' <- NULL
D4$'2004' <- NULL
D4$'2005' <- NULL
D4$'2006' <- NULL
D4$'2007' <- NULL
D4$'2008' <- NULL
D4$'2009' <- NULL
D4$'2010' <- NULL
D4$'2011' <- NULL
D4$'2012' <- NULL
D4$'2013' <- NULL

# Create 
D4[, 3] <- round(log(D4[, 3]), digits = 2)
```

# Variation in Perceived Opportunities in OECD
```{r echo =FALSE, cache=TRUE, include=TRUE, results='asis'}
# Plot
Opp_map <- gvisGeoChart(D4, locationvar = 'iso2c',
                      colorvar = 'mean',
                      options = list(
                        colors = "['#fff7bc', '#d95f0e']"
))

print(Opp_map, tag = 'chart')

```

# Distribution of Perceived Opportunities in OECD Countries

```{r echo =FALSE, cache=FALSE, include=TRUE, results='asis', warning=FALSE, error=FALSE, message=FALSE}

D4 %>% 
  ggvis(~mean, fill := "#2c7fb8") %>% 
  layer_histograms(width =  input_slider(0, 2, step = 0.10, label = "width"),
                   center = input_slider(0, 2, step = 0.05, label = "center"))
